Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-03 Paper/results.tex
Added tikZ image labels

In comparison the same case for Nalu-Wind takes 3.404363 seconds per time step which
takes a total of 113.48 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.032 \times 10^{-4}$ s.

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20_samelimits.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20_samelimits.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\

  \includegraphics[height=2.5in]{figures/snapshots/10ms/velh_mag_side.png} \\

  \includegraphics[height=2.5in]{figures/snapshots/15ms/velh_mag_side.png} \\

  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
    velocity, taken at t=20,000 seconds along the wind direction. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In comparison the same case for Nalu-Wind takes 3.404363 seconds per time step which
takes a total of 75.65 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.032 \times 10^{-4}$ s.

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel, 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel, 5 m/s};

    % 10 m/s plots    
    \node[anchor=south west, inner sep=0](image) at (0in,2.25in)
         {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 2.25in){(c) horizontal vel, 10 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
         {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 2.25in){(d) vertical vel, 10 m/s};

    % 15 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,0in)
         {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 0in){(e) horizontal vel, 15 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
         {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 0in){(f) vertical vel, 15 m/s};

  \end{tikzpicture}
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m, for the AMR-Wind calculation of the
    stable 5 m/s, 10 m/s, and 15 m/s ABL. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}         
    \node[anchor=south west, inner sep=0](image) at (0,0in)
         {\includegraphics[height=2.5in]{figures/snapshots/15ms/velh_mag_side.png}};
    \node[align=left] at (2.5in, 0){(c) AMR-Wind stable, 15 m/s};

    \node[anchor=south west, inner sep=0](image) at (0,2.5in)
         {\includegraphics[height=2.5in]{figures/snapshots/10ms/velh_mag_side.png}};
    \node[align=left] at (2.5in, 2.5in){(b) AMR-Wind stable, 10 m/s};

    \node[anchor=south west, inner sep=0](image) at (0,5.0in)
         {\includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png}};
    \node[align=left] at (2.5in, 5.0in){(a) AMR-Wind stable, 5 m/s};
  \end{tikzpicture}
  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
    velocity, taken at t=20,000 seconds along the wind direction, for
    the (a) 5m/s, (b) 10 m/s, and (c) 15 m/s AMR-Wind stable
    calculations }

\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
